---
title: "Phenology Models"
author: "Natalie Love"
date: "9/2/2020"
output: html_document
---

This code is designed to construct a phenoclimatic model (generalized linear model) using a dataset of herbarium specimens that quantifies the sensitivity of the day of year of collection to climate. This model can then be used to predict the DOY under future climatic conditions.
```{r}
library(tidyverse)
library(raster)
library(sp)
library(sf)
library(rgdal)
library(prism)
library(viridis)
library(car)
```


#1. Create long-term mean climate rasters
###1a. Download prism data
4km grid
Only need to do this once!
```{r}
#options(prism.path = "data/PRISM/temp")
#get_prism_annual(type = "tmean",
                 #years = 1895:2013,
                 #keepZip = FALSE)

#options(prism.path = "data/PRISM/ppt")
#get_prism_annual(type = "ppt",
                 #years = 1895:2013,
                 #keepZip = FALSE)
```

###1b. Read in rasters and calculate long-term mean.
1895-1981
```{r}
###TEMPERATURE###
#read in rasters, currently .bil format (years 1985-1980)
list <- list.files(path = "data/PRISM/temp", pattern = "\\.bil$", recursive = TRUE, full.names = TRUE)
list

#create raster stack and rename each layer as a year
MAT_LT_stack <- stack(list)
plot(MAT_LT_stack[[1:10]])
layer_names <- 1895:2013
names(MAT_LT_stack) <- layer_names
names(MAT_LT_stack)

#use bio01 from worldclim data as a template for future transformations of the long-term mean climate data from PRISM
mask <- predictors.cfp[[1]]

#Reproject all layers at once
MAT_LT_stack_repro <- projectRaster(MAT_LT_stack, mask)


#write so we can use these later
writeRaster(MAT_LT_stack_repro, filename = "data/PRISM/MAT_exported/MAT_LT", format = "GTiff", bylayer = TRUE, suffix = "names")

#Calculate mean across all years (1895-1980)
MAT_1895_1970 <- MAT_LT_stack_repro[[1:76]]
names(MAT_1895_1970) #check this is the right years
MAT_LT_1 <- calc(MAT_1895_1970, fun = mean)
plot(MAT_LT_1)

###PPT####
list <- list.files(path = "data/PRISM/ppt", pattern = "\\.bil$", recursive = TRUE, full.names = TRUE)
list
PPT_LT_stack <- stack(list)
names(PPT_LT_stack) <- layer_names
names(PPT_LT_stack)

#reproject entire raster stack and export, going to need these later to extract values
PPT_LT_stack_repro <- projectRaster(PPT_LT_stack, mask)
names(PPT_LT_stack_repro)


#Write these layers so I can access them later
writeRaster(PPT_LT_stack_repro, filename = "data/PRISM/ppt_exported/MAP_LT", format = "GTiff", bylayer = TRUE, suffix = "names")

#Calculate mean across years (1895-1970)
MAP_1895_1970 <- PPT_LT_stack_repro[[1:76]]
names(MAP_1895_1970)
MAP_LT_1 <- calc(MAP_1895_1970, fun = mean)
plot(MAP_LT_1)

#make sure everything matches among rasters
MAT_LT_1
MAP_LT_1
```

##1c. Mask to match other rasters
```{r}
MAT_LT <- mask(MAT_LT_1, mask)
plot(MAT_LT)

MAP_LT <- mask(MAP_LT_1, mask)
plot(MAP_LT)

#write the long-term mean rasters
writeRaster(MAT_LT, filename = "data/PRISM/long_term_mean_rasters/MAT_LT_1895_1970.tif", format = "GTiff")
writeRaster(MAP_LT, filename = "data/PRISM/long_term_mean_rasters/MAP_LT_1895_1970.tif", format = "GTiff")
```
###1d. Plots to explore similarities between climate datasources
```{r}
plot(MAT_LT - predictors.cfp[[1]])
MAT_diff <- MAT_LT - predictors.cfp[[1]]
hist(MAT_diff)

plot(MAP_LT - predictors.cfp[[5]])
MAP_diff <- MAP_LT - predictors.cfp[[5]]
hist(MAP_diff)
```


#2. Extract long-term mean values and YOC values and then calculate anomalies
##2a. Bring in cleaned herbarium data
```{r}
#coordinates in columns latitude and longitude
tort_herbarium_1 <- read_csv("data/occurrences/all_spec_1902_2013_20perdatafiltered.csv")

#select necessary rows
tort_herbarium <- tort_herbarium_1[,1:27]
```

###2b. Loop to extract YOC collection MAT and MAP values for each collection location and year
```{r}
#create empty dataframe to fill with YOC climate
YOC_MAT <- vector(mode = "double")
YOC_MAP <- vector(mode = "double")


#loop
for(i in 1:nrow(tort_herbarium)){
#first identify year
  YOC <- tort_herbarium$year[i]

#YOC temperature  
  raster_t <- raster(paste("data/PRISM/MAT_exported/MAT_LT_X", YOC, ".tif", sep = ""))
  MAT_val <- raster::extract(raster_t, tort_herbarium[i, c(17,16)])
  YOC_MAT[i] <- MAT_val 
  
#YOC PPT
  raster_p <- raster(paste("data/PRISM/ppt_exported/MAP_LT_X", YOC, ".tif", sep = ""))
  MAP_val <- raster::extract(raster_p, tort_herbarium[i, c(17,16)])
  YOC_MAP[i] <- MAP_val
}


```

###2c. Merge YOC to main dataframe
```{r}
tort_herb_climate <- cbind(tort_herbarium, YOC_MAP, YOC_MAT)

#make sure its there and looks ok
head(tort_herb_climate[1:10,24:29])
```

###2e. Get Long-term mean data values
```{r}
#read in rasters
MAT_LT <- raster("data/PRISM/long_term_mean_rasters/MAT_LT_1895_1970.tif")
plot(MAT_LT)

MAP_LT <- raster("data/PRISM/long_term_mean_rasters/MAP_LT_1895_1970.tif")
plot(MAP_LT)

#extract data
MAT_longterm <- raster::extract(MAT_LT, tort_herbarium[,c(17,16)])
MAP_longterm <- raster::extract(MAP_LT, tort_herbarium[,c(17,16)])

#bind to main dataframe
tort_herb_climate <- cbind(tort_herb_climate, MAT_longterm, MAP_longterm)
head(tort_herb_climate[1:10,27:31])

#line drop rows that have NAs for climate variables (i.e., they are outside the CFP)
tort_herb_climate <- tort_herb_climate[!is.na(tort_herb_climate$MAT_longterm),]

```

###2f. Calculate anomalies
```{r}
tort_herb_climate <- tort_herb_climate %>% 
  mutate(MAT_anom = YOC_MAT - MAT_longterm) %>%
  mutate(MAP_anom = YOC_MAP - MAP_longterm)

head(tort_herb_climate)
```
#3. Designate warm vs. cool groups
```{r}
for (i in 1:nrow(tort_herb_climate)){
  if (tort_herb_climate$MAT_longterm[i] <= median(tort_herb_climate$MAT_longterm)){
  tort_herb_climate$temp_group[i] <- "C"  
  } else {tort_herb_climate$temp_group[i] <- "W"}
}  

#check if that worked
c <- tort_herb_climate %>% filter(temp_group == "C")
w <- tort_herb_climate %>% filter(temp_group == "W")


max(c$MAT_longterm) #max MAT at cool sites should be less than or equal to median MAT
min(w$MAT_longterm) #min MAT at warm sites should be just greater than median MAT

```


#4. Construct phenoclimatic model
```{r}
cool_lm <- lm(DOY ~ 
     PI +
     MAT_longterm +
     MAP_longterm +
     MAT_anom +
     MAP_anom,
   data = c)

warm_lm <- lm(DOY ~ 
     PI +
     MAT_longterm +
     MAP_longterm +
     MAT_anom +
     MAP_anom,
   data = w)
  
#full model  
lm1 <- lm(DOY ~ 
     PI +
     MAT_longterm +
     MAP_longterm +
     MAT_anom +
     MAP_anom +
     temp_group +
     temp_group*MAT_longterm,
   data = tort_herb_climate)

summary(cool_lm)
summary(warm_lm)

#check VIF (everything is less than 2)
vif(cool_lm)
vif(warm_lm)
```

##5. Create cool vs. warm region raster
Need to create a binary raster with cool warm regions then mask to the current distribution of S. tortuosus
Warm = 3
Cool = 2
```{r}
cwregion_raster <- predictors.cfp[[1]]
cwregion_raster[cwregion_raster <= median(tort_herb_climate$MAT_longterm)] <- 2
cwregion_raster[cwregion_raster > median(tort_herb_climate$MAT_longterm)] <- 3

plot(cwregion_raster)

#create copy of binary mask so I can make a mask where the CFP outside the range (where values = 0) become NA
binary_px_mask <- binary_px
plot(binary_px_mask)

binary_px_mask[binary_px_mask == 0] <- NA
plot(binary_px_mask)

#Mask cool/warm region raster to binary range extent
cwregion_tort <- mask(cwregion_raster, binary_px_mask)
plot(cwregion_tort)

#crop cw_raster to extent of of PRISM data (not in Baja)
cwregion_tort <- crop(cwregion_tort, ext)
plot(cwregion_tort)
```
###5a. Create background layer
Need to make a background layer that represents the CFP for visual purposes
```{r}
bio1[bio1 < 20] <- 1
bio1
plot(bio1)

#rename
cfp_background <- bio1
```

### 5b. Plot with ggplot
```{r}
cwregion_tort_df <- as.data.frame(cwregion_tort, xy = TRUE)
cfp_background_df <- as.data.frame(cfp_background, xy = TRUE)

cwregion_gg <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = cwregion_tort_df, aes(x = x, y = y, fill = as.factor(bio01))) +
  scale_fill_manual(name = "Temperature Region", values = c("#4393C3","#D6604D","transparent"), labels = c("cool","warm","")) +
  coord_sf() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme_bw(base_size = 14)

cwregion_gg


```

#6. Future climate scenarios: Read in, make anomaly layers
Need to read in MAT and MAP layers (bio01 and bio12, respectively) and then use them to create anomaly layers
```{r}
###BCC###
#BCC 245 2021-2040
BCC_245_2021_MAT <- raster("data/future_climate/BCC_245_2021/bio01.tif")
BCC_245_2021_MAP <- raster("data/future_climate/BCC_245_2021/bio12.tif")

#BCC 245 2081-2100
BCC_245_2081_MAT <- raster("data/future_climate/BCC_245_2081/bio01.tif")
BCC_245_2081_MAP <- raster("data/future_climate/BCC_245_2081/bio12.tif")

#BCC 585 2021-2040
BCC_585_2021_MAT <- raster("data/future_climate/BCC_585_2021/bio01.tif")
BCC_585_2021_MAP <- raster("data/future_climate/BCC_585_2021/bio12.tif")

#BCC 585 2081-2100
BCC_585_2081_MAT <- raster("data/future_climate/BCC_585_2081/bio01.tif")
BCC_585_2081_MAP <- raster("data/future_climate/BCC_585_2081/bio12.tif")

####CNRM#####
#CNRM 245 2021-2040
CNRM_245_2021_MAT <- raster("data/future_climate/CNRM_245_2021/bio01.tif")
CNRM_245_2021_MAP <- raster("data/future_climate/CNRM_245_2021/bio12.tif")

#CNRM 245 2081-2100
CNRM_245_2081_MAT <- raster("data/future_climate/CNRM_245_2081/bio01.tif")
CNRM_245_2081_MAP <- raster("data/future_climate/CNRM_245_2081/bio12.tif")

#CNRM 585 2021-2040
CNRM_585_2021_MAT <- raster("data/future_climate/CNRM_585_2021/bio01.tif")
CNRM_585_2021_MAP <- raster("data/future_climate/CNRM_585_2021/bio12.tif")

#CNRM 585 2081-2100
CNRM_585_2081_MAT <- raster("data/future_climate/CNRM_585_2081/bio01.tif")
CNRM_585_2081_MAP <- raster("data/future_climate/CNRM_585_2081/bio12.tif")
```

###6a. Create anomaly layers for BCC Model
Long-term mean layers are MAT_LT and MAP_LT. I also need to rename the raster layer within the raster metadata using `names()` so that when I use the predict function, it will know which variable matches with which layer
Names in the model are:
MAT_longterm
MAP_longterm
MAT_anom
MAP_anom
```{r}
###BCC###
#BCC 245 2021-2040
BCC_245_2021_MATanom <- BCC_245_2021_MAT - MAT_LT
names(BCC_245_2021_MATanom) <- "MAT_anom"
plot(BCC_245_2021_MATanom)
hist(BCC_245_2021_MATanom)

BCC_245_2021_MAPanom <- BCC_245_2021_MAP - MAP_LT
names(BCC_245_2021_MAPanom) <- "MAP_anom"
plot(BCC_245_2021_MAPanom)
hist(BCC_245_2021_MAPanom)

#BCC 245 2081-2100
BCC_245_2081_MATanom <- BCC_245_2081_MAT - MAT_LT
names(BCC_245_2081_MATanom) <- "MAT_anom"
plot(BCC_245_2081_MATanom)
hist(BCC_245_2081_MATanom)

BCC_245_2081_MAPanom <- BCC_245_2081_MAP - MAP_LT
names(BCC_245_2081_MAPanom) <- "MAP_anom"
plot(BCC_245_2081_MAPanom)
hist(BCC_245_2081_MAPanom)

#BCC 585 2021-2040
BCC_585_2021_MATanom <- BCC_585_2021_MAT - MAT_LT
names(BCC_585_2021_MATanom) <- "MAT_anom"
plot(BCC_585_2021_MATanom)
hist(BCC_585_2021_MATanom)

BCC_585_2021_MAPanom <- BCC_585_2021_MAP - MAP_LT
names(BCC_585_2021_MAPanom) <- "MAP_anom"
plot(BCC_585_2021_MAPanom)
hist(BCC_585_2021_MAPanom)

#BCC 585 2081-2100
BCC_585_2081_MATanom <- BCC_585_2081_MAT - MAT_LT
names(BCC_585_2081_MATanom) <- "MAT_anom"
plot(BCC_585_2081_MATanom)
hist(BCC_585_2081_MATanom)

BCC_585_2081_MAPanom <- BCC_585_2081_MAP - MAP_LT
names(BCC_585_2081_MAPanom) <- "MAP_anom"
plot(BCC_585_2081_MAPanom)
hist(BCC_585_2081_MAPanom)
```

###6b. Create anomaly layers for CNRM
Long-term mean layers are MAT_LT and MAP_LT. I also need to rename the raster layer within the raster metadata using `names()` so that when I use the predict function, it will know which variable matches with which layer
Names in the model are:
MAT_longterm
MAP_longterm
MAT_anom
MAP_anom
```{r}
###CNRM###
#CNRM 245 2021-2040
CNRM_245_2021_MATanom <- CNRM_245_2021_MAT - MAT_LT
names(CNRM_245_2021_MATanom) <- "MAT_anom"
plot(CNRM_245_2021_MATanom)
hist(CNRM_245_2021_MATanom)

CNRM_245_2021_MAPanom <- CNRM_245_2021_MAP - MAP_LT
names(CNRM_245_2021_MAPanom) <- "MAP_anom"
plot(CNRM_245_2021_MAPanom)
hist(CNRM_245_2021_MAPanom)

#CNRM 245 2081-2100
CNRM_245_2081_MATanom <- CNRM_245_2081_MAT - MAT_LT
names(CNRM_245_2081_MATanom) <- "MAT_anom"
plot(CNRM_245_2081_MATanom)
hist(CNRM_245_2081_MATanom)

CNRM_245_2081_MAPanom <- CNRM_245_2081_MAP - MAP_LT
names(CNRM_245_2081_MAPanom) <- "MAP_anom"
plot(CNRM_245_2081_MAPanom)
hist(CNRM_245_2081_MAPanom)

#CNRM 585 2021-2040
CNRM_585_2021_MATanom <- CNRM_585_2021_MAT - MAT_LT
names(CNRM_585_2021_MATanom) <- "MAT_anom"
plot(CNRM_585_2021_MATanom)
hist(CNRM_585_2021_MATanom)

CNRM_585_2021_MAPanom <- CNRM_585_2021_MAP - MAP_LT
names(CNRM_585_2021_MAPanom) <- "MAP_anom"
plot(CNRM_585_2021_MAPanom)
hist(CNRM_585_2021_MAPanom)

#CNRM 585 2081-2100
CNRM_585_2081_MATanom <- CNRM_585_2081_MAT - MAT_LT
names(CNRM_585_2081_MATanom) <- "MAT_anom"
plot(CNRM_585_2081_MATanom)
hist(CNRM_585_2081_MATanom)

CNRM_585_2081_MAPanom <- CNRM_585_2081_MAP - MAP_LT
names(CNRM_585_2081_MAPanom) <- "MAP_anom"
plot(CNRM_585_2081_MAPanom)
hist(CNRM_585_2081_MAPanom)
```
###6c. Create anomalies for current climate
Not totally sure what to use here but currently using WorldClim 1970-2000 averages
```{r}
bio01 <- predictors.cfp[[1]]
bio12 <- predictors.cfp[[5]]

bio01_anom <- bio01 - MAT_LT
names(bio01_anom) <- "MAT_anom"
plot(bio01_anom)
hist(bio01_anom)

bio12_anom <- bio12 - MAP_LT
names(bio12_anom) <- "MAP_anom"
plot(bio12_anom)
hist(bio12_anom)
```


##6d. Re-name long-term mean layers to match model
```{r}
names(MAT_LT) <- "MAT_longterm"
names(MAP_LT) <- "MAP_longterm"
```

#7 Make a raster to represent peak flower and peak fruit
Use CFP background, replace 1s with 2.5 and 4
flower PI = 2.5
fruit PI = 4
```{r}
PI_flower <- cfp_background
PI_fruit <- cfp_background

PI_flower[PI_flower == 1] <- 2.5
names(PI_flower) <- "PI"

PI_fruit[PI_fruit == 1] <- 4
names(PI_fruit) <- "PI"
```

#8. Long-term mean and PI rasters rasters so everything is the same extent
```{r}
MAT_LT <- crop(MAT_LT, BCC_245_2021_MAPanom)
plot(MAT_LT)

MAP_LT <- crop(MAP_LT, BCC_245_2021_MAPanom)
plot(MAP_LT)

ext <- extent(BCC_245_2021_MAP)
PI_flower <- mask(PI_flower, MAT_LT)
PI_flower <- crop(PI_flower, ext)
plot(PI_flower)

PI_fruit <- mask(PI_fruit, MAT_LT)
PI_fruit <- crop(PI_fruit, ext)
plot(PI_fruit)
```

#9. Create Raster stacks for one current and each future time period 
I'm not sure if it matters, but I am going to stack them in the same order they appear in the model
PI
MAT_longterm
MAP_longterm
MAT_anom
MAP_anom

###9a. Current climate
```{r}
current_fl <- stack(PI_flower, MAT_LT, MAP_LT, bio01_anom, bio12_anom)
names(current_fl)
```


###9b. BCC Models
```{r}
BCC_245_2021_fl <- stack(PI_flower, BCC_245_2021_MATanom, BCC_245_2021_MAPanom, MAT_LT, MAP_LT)
#check that the names are correct
names(BCC_245_2021_fl)

BCC_245_2081_fl <- stack(PI_flower, BCC_245_2081_MATanom, BCC_245_2081_MAPanom, MAT_LT, MAP_LT)
names(BCC_245_2081_fl)

BCC_585_2021_fl <- stack(PI_flower, BCC_585_2021_MATanom, BCC_585_2021_MAPanom, MAT_LT, MAP_LT)
names(BCC_585_2021_fl)

BCC_585_2081_fl <- stack(PI_flower, BCC_585_2081_MATanom, BCC_585_2081_MAPanom, MAT_LT, MAP_LT)
names(BCC_585_2081_fl)
```

###9c. CNRM Models
```{r}
CNRM_245_2021_fl <- stack(PI_flower, CNRM_245_2021_MATanom, CNRM_245_2021_MAPanom, MAT_LT, MAP_LT)
names(CNRM_245_2021_fl)

CNRM_245_2081_fl <- stack(PI_flower, CNRM_245_2081_MATanom, CNRM_245_2081_MAPanom, MAT_LT, MAP_LT)
names(CNRM_245_2081_fl)

CNRM_585_2021_fl <- stack(PI_flower, CNRM_585_2021_MATanom, CNRM_585_2021_MAPanom, MAT_LT, MAP_LT)
names(CNRM_585_2021_fl)

CNRM_585_2081_fl <- stack(PI_flower, CNRM_585_2081_MATanom, CNRM_585_2081_MAPanom, MAT_LT, MAP_LT)
names(CNRM_585_2081_fl)
```


#10. Predict DOY based on future climate conditions
###10a. Make Prediction on current climate
```{r}
current_fl_DOY_c <- raster::predict(object = current_fl,
                                    model = cool_lm)

plot(current_fl_DOY_c)

current_fl_DOY_w <- raster::predict(object = current_fl,
                                       model = warm_lm)

plot(current_fl_DOY_w)



#make DF for ggplot
current_fl_DOY_c_df <- as.data.frame(current_fl_DOY_c, xy = TRUE)
current_fl_DOY_w_df <- as.data.frame(current_fl_DOY_w, xy = TRUE)

#ggplot, DOY 94-272
current_fl_DOY_c_gg <- ggplot() +
  geom_raster(data = current_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(94,272), na.value = "transparent", name = "DOY", option = "C", direction = -1) +
  coord_sf() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme_bw()

current_fl_DOY_c_gg

current_fl_DOY_w_gg <- ggplot() +
  geom_raster(data = current_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(94,272), na.value = "transparent", name = "DOY", option = "C", direction = -1) +
  coord_sf() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme_bw()

current_fl_DOY_w_gg

current_fl_DOY_gg <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = current_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = current_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(94,272), na.value = "transparent", name = "DOY", option = "C", direction = -1) +
  coord_sf() +
  xlab("Longitude") +
  ylab("Latitude") +
  theme_bw()

current_fl_DOY_gg


#mask to cool vs warm region rasters
current_fl_DOY_c <- mask(current_fl_DOY_c, coolregion_raster)
current_fl_DOY_w <- mask(current_fl_DOY_w, warmregion_raster)

hist(current_fl_DOY_c)
hist(current_fl_DOY_w)

```


####10b. Make prediction on future climate: BCC
```{r}
#BCC 245 2021
BCC_245_2021_fl_DOY_c <- raster::predict(object = BCC_245_2021_fl,
                                       model = cool_lm)
plot(BCC_245_2021_fl_DOY_c)


BCC_245_2021_fl_DOY_w <- raster::predict(object = BCC_245_2021_fl,
                                       model = warm_lm)

plot(BCC_245_2021_fl_DOY_w)

#BCC 245 2081
BCC_245_2081_fl_DOY_c <- raster::predict(object = BCC_245_2081_fl,
                                       model = cool_lm)
plot(BCC_245_2081_fl_DOY_c)

BCC_245_2081_fl_DOY_w <- raster::predict(object = BCC_245_2081_fl,
                                       model = warm_lm)

plot(BCC_245_2081_fl_DOY_w)

#BCC 585 2021
BCC_585_2021_fl_DOY_c <- raster::predict(object = BCC_585_2021_fl,
                                       model = cool_lm)
plot(BCC_585_2021_fl_DOY_c)


BCC_585_2021_fl_DOY_w <- raster::predict(object = BCC_585_2021_fl,
                                       model = warm_lm)

plot(BCC_585_2021_fl_DOY_w)

#BCC 585 2081
BCC_585_2081_fl_DOY_c <- raster::predict(object = BCC_585_2081_fl,
                                       model = cool_lm)
plot(BCC_585_2081_fl_DOY_c)


BCC_585_2081_fl_DOY_w <- raster::predict(object = BCC_585_2081_fl,
                                       model = warm_lm)

plot(BCC_585_2081_fl_DOY_w)

```
###10c. Make future predictions CNRM
```{r}
#CNRM 245 2021
CNRM_245_2021_fl_DOY_c <- raster::predict(object = CNRM_245_2021_fl,
                                       model = cool_lm)
plot(CNRM_245_2021_fl_DOY_c)

CNRM_245_2021_fl_DOY_w <- raster::predict(object = CNRM_245_2021_fl,
                                       model = warm_lm)
plot(CNRM_245_2021_fl_DOY_w)

#CNRM 245 2081-2100
CNRM_245_2081_fl_DOY_c <- raster::predict(object = CNRM_245_2081_fl,
                                       model = cool_lm)
plot(CNRM_245_2081_fl_DOY_c)

CNRM_245_2081_fl_DOY_w <- raster::predict(object = CNRM_245_2081_fl,
                                       model = warm_lm)
plot(CNRM_245_2081_fl_DOY_w)

#CNRM 585 2021
CNRM_585_2021_fl_DOY_c <- raster::predict(object = CNRM_585_2021_fl,
                                       model = cool_lm)
plot(CNRM_585_2021_fl_DOY_c)

CNRM_585_2021_fl_DOY_w <- raster::predict(object = CNRM_585_2021_fl,
                                       model = warm_lm)
plot(CNRM_585_2021_fl_DOY_w)

#CNRM 585 2081
CNRM_585_2081_fl_DOY_c <- raster::predict(object = CNRM_585_2081_fl,
                                       model = cool_lm)
plot(CNRM_585_2081_fl_DOY_c)

CNRM_585_2081_fl_DOY_w <- raster::predict(object = CNRM_585_2081_fl,
                                       model = warm_lm)
plot(CNRM_585_2081_fl_DOY_w)
```


#11. Calculate change in DOY for each future time period
Future layer - current layer = change in DOY
Negative values represent advancement

#11a. Change in DOY - BCC
```{r}
#BCC 245 2021-2040
change_BCC_245_2021_fl_DOY_c <- BCC_245_2021_fl_DOY_c - current_fl_DOY_c
plot(change_BCC_245_2021_fl_DOY_c)

change_BCC_245_2021_fl_DOY_w <- BCC_245_2021_fl_DOY_w - current_fl_DOY_w
plot(change_BCC_245_2021_fl_DOY_w)

#BCC 245 2081-2100
change_BCC_245_2081_fl_DOY_c <- BCC_245_2081_fl_DOY_c - current_fl_DOY_c
plot(change_BCC_245_2081_fl_DOY_c)

change_BCC_245_2081_fl_DOY_w <- BCC_245_2081_fl_DOY_w - current_fl_DOY_w
plot(change_BCC_245_2081_fl_DOY_w)

#BCC 585 2021
change_BCC_585_2021_fl_DOY_c <- BCC_585_2021_fl_DOY_c - current_fl_DOY_c
plot(change_BCC_585_2021_fl_DOY_c)

change_BCC_585_2021_fl_DOY_w <- BCC_585_2021_fl_DOY_w - current_fl_DOY_w
plot(change_BCC_585_2021_fl_DOY_w)


#BCC 585 2081
change_BCC_585_2081_fl_DOY_c <- BCC_585_2081_fl_DOY_c - current_fl_DOY_c
plot(change_BCC_585_2081_fl_DOY_c)

change_BCC_585_2081_fl_DOY_w <- BCC_585_2081_fl_DOY_w - current_fl_DOY_w
plot(change_BCC_585_2081_fl_DOY_w)
```
###11b. CNRM Change in DOY
```{r}
#CNRM 245 2021-2040
change_CNRM_245_2021_fl_DOY_c <- CNRM_245_2021_fl_DOY_c - current_fl_DOY_c
plot(change_CNRM_245_2021_fl_DOY_c)

change_CNRM_245_2021_fl_DOY_w <- CNRM_245_2021_fl_DOY_w - current_fl_DOY_w
plot(change_CNRM_245_2021_fl_DOY_w)

#CNRM 245 2081-2100
change_CNRM_245_2081_fl_DOY_c <- CNRM_245_2081_fl_DOY_c - current_fl_DOY_c
plot(change_CNRM_245_2081_fl_DOY_c)

change_CNRM_245_2081_fl_DOY_w <- CNRM_245_2081_fl_DOY_w - current_fl_DOY_w
plot(change_CNRM_245_2081_fl_DOY_w)

#CNRM 585 2021-2040
change_CNRM_585_2021_fl_DOY_c <- CNRM_585_2021_fl_DOY_c - current_fl_DOY_c
plot(change_CNRM_585_2021_fl_DOY_c)

change_CNRM_585_2021_fl_DOY_w <- CNRM_585_2021_fl_DOY_w - current_fl_DOY_w
plot(change_CNRM_585_2021_fl_DOY_w)

#CNRM 585 2081-100
change_CNRM_585_2081_fl_DOY_c <- CNRM_585_2081_fl_DOY_c - current_fl_DOY_c
plot(change_CNRM_585_2081_fl_DOY_c)

change_CNRM_585_2081_fl_DOY_w <- CNRM_585_2081_fl_DOY_w - current_fl_DOY_w
plot(change_CNRM_585_2081_fl_DOY_w)
```


#12. Mask to cool and warm region raster
###12a. First need to make a raster that represents warm region and one that represents cool region in current climate
```{r}
plot(cwregion_raster)

#make it so it only has 2's which represent grids with cool regions
coolregion_raster <- cwregion_raster
coolregion_raster[coolregion_raster == 3] <- NA
coolregion_raster <- mask(coolregion_raster, binary_px_mask)
plot(coolregion_raster)

#make it so it only has 3's which represent grids with warm regions
warmregion_raster <- cwregion_raster
warmregion_raster[warmregion_raster == 2] <- NA
warmregion_raster <- mask(warmregion_raster, binary_px_mask)
plot(warmregion_raster)

```
###12b. Make warm/cool region masks for BCC scenarios
Binary future rasters are stored in binary_future_rasters stack
```{r}
names(binary_future_rasters)
binary_BCC_245_2021 <- binary_future_rasters[[1]]
binary_BCC_245_2081 <- binary_future_rasters[[2]]
binary_BCC_585_2021 <- binary_future_rasters[[3]]
binary_BCC_585_2081 <- binary_future_rasters[[4]]

#make 0's (absense) to NAs so the mask will work properly
binary_BCC_245_2021[binary_BCC_245_2021 == 0] <- NA
binary_BCC_245_2081[binary_BCC_245_2081 == 0] <- NA
binary_BCC_585_2021[binary_BCC_585_2021 == 0] <- NA
binary_BCC_585_2081[binary_BCC_585_2081 == 0] <- NA

#BCC 245 2021-2040
cwregion_BCC2452021 <- mask(x = cwregion_tort, mask = binary_BCC_245_2021)
plot(cwregion_BCC2452021)

#BCC 245 2081-2040
cwregion_BCC2452081 <- mask(x = cwregion_tort, mask = binary_BCC_245_2081)
plot(cwregion_BCC2452081)

#BCC 585 2021-2040
cwregion_BCC5852021 <- mask(x = cwregion_tort, mask = binary_BCC_585_2021)
plot(cwregion_BCC5852021)

#BCC 585 2081-2100
cwregion_BCC5852081 <- mask(x = cwregion_tort, mask = binary_BCC_585_2081)
plot(cwregion_BCC5852081)
```

###12c. Make warm/cool region masks for CNRM Scenarios
```{r}
names(binary_future_rasters)

binary_CNRM_245_2021 <- binary_future_rasters[[5]]
binary_CNRM_245_2081 <- binary_future_rasters[[6]]
binary_CNRM_585_2021 <- binary_future_rasters[[7]]
binary_CNRM_585_2081 <- binary_future_rasters[[8]]

#change 0's to NAs so the mask will work properly
binary_CNRM_245_2021[binary_CNRM_245_2021 == 0] <- NA
binary_CNRM_245_2081[binary_CNRM_245_2081 == 0] <- NA
binary_CNRM_585_2021[binary_CNRM_585_2021 == 0] <- NA
binary_CNRM_585_2081[binary_CNRM_585_2081 == 0] <- NA

#create warm/cool region rasters for range extent under each CC scenario
#CNRM 245 2021 
cwregion_CNRM2452021 <- mask(cwregion_tort, mask = binary_CNRM_245_2021)
plot(cwregion_CNRM2452021)

#CNRM 245 2081
cwregion_CNRM2452081 <- mask(cwregion_tort, mask = binary_CNRM_245_2081)
plot(cwregion_CNRM2452081)

#CNRM 585 2021
cwregion_CNRM5852021 <- mask(cwregion_tort, mask = binary_CNRM_585_2021)
plot(cwregion_CNRM5852021)

#CNRM 585 2081
cwregion_CNRM5852081 <- mask(cwregion_tort, mask = binary_CNRM_585_2081)
plot(cwregion_CNRM5852081)
```
###12d.Create seperate warm and cool region raster masks for each scenario - BCC
2 = cool regions
3 = warm regions
Need to replace 2 with NA for only warm region raster and 3 with NA for only cool region rasters
```{r}
#BCC 245 2021-2040
cwregion_BCC2452021_c <- cwregion_BCC2452021
cwregion_BCC2452021_w <- cwregion_BCC2452021

cwregion_BCC2452021_c[cwregion_BCC2452021_c == 3] <- NA
cwregion_BCC2452021_w[cwregion_BCC2452021_w == 2] <- NA

plot(cwregion_BCC2452021_c)
plot(cwregion_BCC2452021_w)

#BCC 245 2081-2100
cwregion_BCC2452081_c <- cwregion_BCC2452081
cwregion_BCC2452081_w <- cwregion_BCC2452081

cwregion_BCC2452081_c[cwregion_BCC2452081_c == 3] <- NA
cwregion_BCC2452081_w[cwregion_BCC2452081_w == 2] <- NA

plot(cwregion_BCC2452081_c)
plot(cwregion_BCC2452081_w)

#BCC 585 2021-2040
cwregion_BCC5852021_c <- cwregion_BCC5852021
cwregion_BCC5852021_w <- cwregion_BCC5852021

cwregion_BCC5852021_c[cwregion_BCC5852021_c == 3] <- NA
cwregion_BCC5852021_w[cwregion_BCC5852021_w == 2] <- NA

plot(cwregion_BCC5852021_c)
plot(cwregion_BCC5852021_w)

#BCC 585 2081-2100
cwregion_BCC5852081_c <- cwregion_BCC5852081
cwregion_BCC5852081_w <- cwregion_BCC5852081

cwregion_BCC5852081_c[cwregion_BCC5852081_c == 3] <- NA
cwregion_BCC5852081_w[cwregion_BCC5852081_w == 2] <- NA

plot(cwregion_BCC5852081_c)
plot(cwregion_BCC5852081_w)
```

###12e.Create seperate warm and cool region rasters for each CNRM scenario
```{r}
#CNRM 245 2021-2040
cwregion_CNRM2452021_c <- cwregion_CNRM2452021
cwregion_CNRM2452021_w <- cwregion_CNRM2452021

cwregion_CNRM2452021_c[cwregion_CNRM2452021_c == 3] <- NA
cwregion_CNRM2452021_w[cwregion_CNRM2452021_w == 2] <- NA

plot(cwregion_CNRM2452021_c)
plot(cwregion_CNRM2452021_w)

#CNRM 245 2081-2100
cwregion_CNRM2452081_c <- cwregion_CNRM2452081
cwregion_CNRM2452081_w <- cwregion_CNRM2452081

cwregion_CNRM2452081_c[cwregion_CNRM2452081_c == 3] <- NA
cwregion_CNRM2452081_w[cwregion_CNRM2452081_w == 2] <- NA

plot(cwregion_CNRM2452081_c)
plot(cwregion_CNRM2452081_w)

#CNRM 585 2021-2040
cwregion_CNRM5852021_c <- cwregion_CNRM5852021
cwregion_CNRM5852021_w <- cwregion_CNRM5852021

cwregion_CNRM5852021_c[cwregion_CNRM5852021_c == 3] <- NA
cwregion_CNRM5852021_w[cwregion_CNRM5852021_w == 2] <- NA

plot(cwregion_CNRM5852021_c)
plot(cwregion_CNRM5852021_w)

#CNRM 585 2081-2100
cwregion_CNRM5852081_c <- cwregion_CNRM5852081
cwregion_CNRM5852081_w <- cwregion_CNRM5852081

cwregion_CNRM5852081_c[cwregion_CNRM5852081_c == 3] <- NA
cwregion_CNRM5852081_w[cwregion_CNRM5852081_w == 2] <- NA

plot(cwregion_CNRM5852081_c)
plot(cwregion_CNRM5852081_w)
```


###12f. Mask predicted DOY to warm or cool region - BCC
```{r}
#BCC 245 2021-2040
change_BCC_245_2021_fl_DOY_c <- mask(change_BCC_245_2021_fl_DOY_c, cwregion_BCC2452021_c)
plot(change_BCC_245_2021_fl_DOY_c)
hist(change_BCC_245_2021_fl_DOY_c)

change_BCC_245_2021_fl_DOY_w <- mask(change_BCC_245_2021_fl_DOY_w, cwregion_BCC2452021_w)
plot(change_BCC_245_2021_fl_DOY_w)
hist(change_BCC_245_2021_fl_DOY_w)

#BCC 245 2081-2100
change_BCC_245_2081_fl_DOY_c <- mask(change_BCC_245_2081_fl_DOY_c, cwregion_BCC2452081_c)
plot(change_BCC_245_2081_fl_DOY_c)
hist(change_BCC_245_2081_fl_DOY_c)

change_BCC_245_2081_fl_DOY_w <- mask(change_BCC_245_2081_fl_DOY_w, cwregion_BCC2452081_w)
plot(change_BCC_245_2081_fl_DOY_w)
hist(change_BCC_245_2081_fl_DOY_w)

#BCC 585 2021-2040
change_BCC_585_2021_fl_DOY_c <- mask(change_BCC_585_2021_fl_DOY_c, cwregion_BCC5852021_c)
plot(change_BCC_585_2021_fl_DOY_c)
hist(change_BCC_585_2021_fl_DOY_c)

change_BCC_585_2021_fl_DOY_w <- mask(change_BCC_585_2021_fl_DOY_w, cwregion_BCC5852021_w)
plot(change_BCC_585_2021_fl_DOY_w)
hist(change_BCC_585_2021_fl_DOY_w)

#BCC 585 2081-2100
change_BCC_585_2081_fl_DOY_c <- mask(change_BCC_585_2081_fl_DOY_c, cwregion_BCC5852081_c)
plot(change_BCC_585_2081_fl_DOY_c)
hist(change_BCC_585_2081_fl_DOY_c)

change_BCC_585_2081_fl_DOY_w <- mask(change_BCC_585_2081_fl_DOY_w, cwregion_BCC5852081_w)
plot(change_BCC_585_2081_fl_DOY_w)
hist(change_BCC_585_2081_fl_DOY_w)
```

###12g.  Mask predicted DOY to warm or cool region - CNRM
```{r}
#CNRM 245 2021-2040
change_CNRM_245_2021_fl_DOY_c <- mask(change_CNRM_245_2021_fl_DOY_c, cwregion_CNRM2452021_c)
plot(change_CNRM_245_2021_fl_DOY_c)
hist(change_CNRM_245_2021_fl_DOY_c)

change_CNRM_245_2021_fl_DOY_w <- mask(change_CNRM_245_2021_fl_DOY_w, cwregion_CNRM2452021_w)
plot(change_CNRM_245_2021_fl_DOY_w)
hist(change_CNRM_245_2021_fl_DOY_w)

#CNRM 245 2081-2100
change_CNRM_245_2081_fl_DOY_c <- mask(change_CNRM_245_2081_fl_DOY_c, cwregion_CNRM2452081_c)
plot(change_CNRM_245_2081_fl_DOY_c)
hist(change_CNRM_245_2081_fl_DOY_c)

change_CNRM_245_2081_fl_DOY_w <- mask(change_CNRM_245_2081_fl_DOY_w, cwregion_CNRM2452081_w)
plot(change_CNRM_245_2081_fl_DOY_w)
hist(change_CNRM_245_2081_fl_DOY_w)

#CNRM 585 2021-2040
change_CNRM_585_2021_fl_DOY_c <- mask(change_CNRM_585_2021_fl_DOY_c, cwregion_CNRM5852021_c)
plot(change_CNRM_585_2021_fl_DOY_c)
hist(change_CNRM_585_2021_fl_DOY_c)

change_CNRM_585_2021_fl_DOY_w <- mask(change_CNRM_585_2021_fl_DOY_w, cwregion_CNRM5852021_w)
plot(change_CNRM_585_2021_fl_DOY_w)
hist(change_CNRM_585_2021_fl_DOY_w)

#CNRM 585 2021-2040
change_CNRM_585_2081_fl_DOY_c <- mask(change_CNRM_585_2081_fl_DOY_c, cwregion_CNRM5852081_c)
plot(change_CNRM_585_2081_fl_DOY_c)
hist(change_CNRM_585_2081_fl_DOY_c)

change_CNRM_585_2081_fl_DOY_w <- mask(change_CNRM_585_2081_fl_DOY_w, cwregion_CNRM5852081_w)
plot(change_CNRM_585_2081_fl_DOY_w)
hist(change_CNRM_585_2081_fl_DOY_w)
```


#13. Plot change in DOY with ggplot
#13a. Create dataframes to plot with ggplot - BCC
```{r}
#BCC 245 2021-2040
change_BCC_245_2021_fl_DOY_c_df <- as.data.frame(change_BCC_245_2021_fl_DOY_c, xy = TRUE)
change_BCC_245_2021_fl_DOY_w_df <- as.data.frame(change_BCC_245_2021_fl_DOY_w, xy = TRUE)

#BCC 245 2081-2100
change_BCC_245_2081_fl_DOY_c_df <- as.data.frame(change_BCC_245_2081_fl_DOY_c, xy = TRUE)
change_BCC_245_2081_fl_DOY_w_df <- as.data.frame(change_BCC_245_2081_fl_DOY_w, xy = TRUE)

#BCC 585 2021-2040
change_BCC_585_2021_fl_DOY_c_df <- as.data.frame(change_BCC_585_2021_fl_DOY_c, xy = TRUE)
change_BCC_585_2021_fl_DOY_w_df <- as.data.frame(change_BCC_585_2021_fl_DOY_w, xy = TRUE)

#BCC 585 2081-2100
change_BCC_585_2081_fl_DOY_c_df <- as.data.frame(change_BCC_585_2081_fl_DOY_c, xy = TRUE)
change_BCC_585_2081_fl_DOY_w_df <- as.data.frame(change_BCC_585_2081_fl_DOY_w, xy = TRUE)
```

###13b. Create dataframes to plot with ggplot - CNRM
```{r}
#CNRM 245 2021-2040
change_CNRM_245_2021_fl_DOY_c_df <- as.data.frame(change_CNRM_245_2021_fl_DOY_c, xy = TRUE)
change_CNRM_245_2021_fl_DOY_w_df <- as.data.frame(change_CNRM_245_2021_fl_DOY_w, xy = TRUE)

#CNRM 245 2081-2100
change_CNRM_245_2081_fl_DOY_c_df <- as.data.frame(change_CNRM_245_2081_fl_DOY_c, xy = TRUE)
change_CNRM_245_2081_fl_DOY_w_df <- as.data.frame(change_CNRM_245_2081_fl_DOY_w, xy = TRUE)

#CNRM 585 2021-2040
change_CNRM_585_2021_fl_DOY_c_df <- as.data.frame(change_CNRM_585_2021_fl_DOY_c, xy = TRUE)
change_CNRM_585_2021_fl_DOY_w_df <- as.data.frame(change_CNRM_585_2021_fl_DOY_w, xy = TRUE)

#CNRM 585 2021-2040
change_CNRM_585_2081_fl_DOY_c_df <- as.data.frame(change_CNRM_585_2081_fl_DOY_c, xy = TRUE)
change_CNRM_585_2081_fl_DOY_w_df <- as.data.frame(change_CNRM_585_2081_fl_DOY_w, xy = TRUE)
```


###13c. Read in CFP and make plottable polygon
```{r}
cfp_multipoly <- st_read("CFP_GIS/CFP_GIS.shp")
crs(cfp_multipoly)

st_is_longlat(cfp_multipoly)

cfp_multipoly_trans <- st_transform(cfp_multipoly, crs(cfp_background))
cfp_multipoly_trans
```


###13d.Plot with ggplot - BCC
-6 to -47
```{r}
##BCC 245 2021-2040
DOY_BCC_245_2021_fl <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = change_BCC_245_2021_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = change_BCC_245_2021_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(-47,-6), na.value = "transparent", name = "Change in DOY", option = "C", direction = -1) +
  coord_sf() +
  theme_bw()

DOY_BCC_245_2021_fl

##BCC 245 2081-2100
DOY_BCC_245_2081_fl <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = change_BCC_245_2081_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = change_BCC_245_2081_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(-47,-6), na.value = "transparent", name = "Change in DOY", option = "C", direction = -1) +
  coord_sf() +
  theme_bw()

DOY_BCC_245_2081_fl

##BCC 585 2021-2040
DOY_BCC_585_2021_fl <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = change_BCC_585_2021_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = change_BCC_585_2021_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(-47,-6), na.value = "transparent", name = "Change in DOY", option = "C", direction = -1) +
  coord_sf() +
  theme_bw()

DOY_BCC_585_2021_fl

##BCC 585 2081-2100
DOY_BCC_585_2081_fl <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = change_BCC_585_2081_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = change_BCC_585_2081_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(-47,-6), na.value = "transparent", name = "Change in DOY", option = "C", direction = -1) +
  coord_sf() +
  theme_bw()

DOY_BCC_585_2081_fl
```

###133. Plot with ggplot - CNRM
```{r}
##CNRM 245 2021-2040
DOY_CNRM_245_2021_fl <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = change_CNRM_245_2021_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = change_CNRM_245_2021_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(-47,-6), na.value = "transparent", name = "Change in DOY", option = "C", direction = -1) +
  coord_sf() +
  theme_bw()

DOY_CNRM_245_2021_fl

##CNRM 245 2081-2100
DOY_CNRM_245_2081_fl <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = change_CNRM_245_2081_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = change_CNRM_245_2081_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(-47,-6), na.value = "transparent", name = "Change in DOY", option = "C", direction = -1) +
  coord_sf() +
  theme_bw()

DOY_CNRM_245_2081_fl

##CNRM 585 2021-2040
DOY_CNRM_585_2021_fl <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = change_CNRM_585_2021_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = change_CNRM_585_2021_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(-47,-6), na.value = "transparent", name = "Change in DOY", option = "C", direction = -1) +
  coord_sf() +
  theme_bw()

DOY_CNRM_585_2021_fl

##CNRM 585 2081-2100
DOY_CNRM_585_2081_fl <- ggplot() +
  geom_sf(data = cfp_multipoly_trans, lwd = 0) +
  geom_raster(data = change_CNRM_585_2081_fl_DOY_c_df, aes(x = x, y = y, fill = layer)) +
  geom_raster(data = change_CNRM_585_2081_fl_DOY_w_df, aes(x = x, y = y, fill = layer)) +
  scale_fill_viridis(limits = c(-47,-6), na.value = "transparent", name = "Change in DOY", option = "C", direction = -1) +
  coord_sf() +
  theme_bw()

DOY_CNRM_585_2081_fl
```

#Histograms
```{r}
hist(change_BCC_245_2021_fl_DOY_c)
hist(change_BCC_245_2021_fl_DOY_w)

hist(change_BCC_245_2081_fl_DOY_c)
hist(change_BCC_245_2081_fl_DOY_w)

hist(change_BCC_585_2021_fl_DOY_c)
hist(change_BCC_585_2021_fl_DOY_w)

hist(change_BCC_585_2081_fl_DOY_c)
hist(change_BCC_585_2081_fl_DOY_w)

```

